---
title: "Interactive Data Exploration Using Shiny"
author: "Connor Claypool"
date: "31 July 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Presenting Exploratory Analyses

Sharing an exploratory analysis as a series of R commands and their outputs, like below, can give lengthy and untidy results.

```{r, echo = FALSE, message = FALSE}
library(dplyr)
```

```{r, comment = ""}
str(iris)
```

... and so on.

## Interactive Exploratory Analysis with Shiny

Alternatively, an exploratory analysis can be packaged in an interactive Shiny app. This brings some key advantages:

- Greater flexibility due to interactive options and dynamic outputs
- Intuitive and easy to understand, even without knowledge of R
- App format allows for convenient organisation with tabs and menus

## App Features

An example exploratory analysis, packaged as a Shiny app, can be accessed [here](https://cclaypool.shinyapps.io/dataexplorer/).

- Tab 1: Data Overview
    - Shows a table of up to 100 observations from the dataset. The user can select how many observations to display and which variable to order the dataset by.
- Tab 2: Exploratory Graphs
    - Allows the user to create a variety of exploratory graphs, including scatter plots, box plots and histograms
    - Users can select which variables to show on the axes and whether to show further variables using color or faceting, and tune graphical options
    
## App Features (cont.)

- Tab 3: Linear Regression
    - Allows the user to fit linear regression models to the data, selecting which variable to model as the outcome and which variables to use as predictors
    - Model coefficients, goodness of fit (adjusted R-Squared) and diagnostic plots are dynamically displayed